Evaluation of performances

### 2020-06-21 analysis/eval-performance.Rmd
wflow_publish(knitr_in("analysis/eval-performance.Rmd"), view = FALSE,     verbose = TRUE)

```{r}
df <- mlr::getBMRPerformances(bm_aggregated_new_buffer2,
  "hr_buffer2", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Laukiz1 = "1", Laukiz2 = "4",
    Luiando = "3", Oiartzun = "2"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Test fold performances for learner SVM on the HR dataset without using a filter. For each row, the model was trained on observations from fold all other plots and tested on the observations of the given plot.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results for any task/learner/filter combination, sorted ascending by RMSE",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Lower ten results for any task/learner/filter combination, sorted decreasing by RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate(Plot = forcats::fct_recode(Plot,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(Plot = as.character(Plot)) %>%
  dplyr::mutate("\\#" = case_when(
    Plot == "Laukiz1" ~ ceiling(`Features (\\%)` * 559),
    Plot == "Laukiz2" ~ ceiling(`Features (\\%)` * 451),
    Plot == "Luiando" ~ ceiling(`Features (\\%)` * 301),
    Plot == "Oiartzun" ~ ceiling(`Features (\\%)` * 497),
  )) %>% 
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, Plot, "Features (\\%)", "\\#", RMSE)

>>>>

```{r}
df <- mlr::getBMRPerformances(bm_aggregated_new_buffer2,
  "hr_buffer2", "SVM MBO No Filter",
  as.df = TRUE
)
df_tab <- df %>%
  dplyr::select(iter, rmse) %>%
  dplyr::rename(Plot = iter, RMSE = rmse) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Laukiz1 = "1", Laukiz2 = "4",
    Luiando = "3", Oiartzun = "2"
  )) %>%
  dplyr::mutate(RMSE = round(RMSE, 2))

df_tab %>%
  xtable::xtable(
    type = "latex",
    caption = "Test fold performances for learner SVM on the HR dataset without using a filter. For each row, the model was trained on observations from all others plots but the given one and tested on the observations of the given plot.",
    label = "tab:svm-single-fold-perf"
  ) %>%
  print(
    file = here::here("docs/00-manuscripts/ieee/performance-svm-single-plot.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table1 %>%
  ungroup() %>%
  arrange(RMSE) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Best ten results among all combinations, sorted in ascending order of RMSE",
    label = "tab:perf-top-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-top-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

# save as latex table
table3 %>%
  ungroup() %>%
  arrange(desc(RMSE)) %>%
  slice(1:10) %>%
  xtable(
    type = "latex",
    caption = "Worst ten results among all combinations, sorted in decreasing order of RMSE",
    label = "tab:perf-worst-10"
  ) %>%
  print(
    file = here("docs/00-manuscripts/ieee/performance-worst-10.tex"),
    include.rownames = TRUE,
    latex.environments = c("center"),
    table.placement = "ht!",
    caption.placement = "top",
    timestamp = NULL
  )

@@

df_tbl <- getBMRTuneResults(bmr_inspect_tune, as.df = TRUE) %>%
  dplyr::rename(Learner = learner.id) %>%
  dplyr::rename(Plot = iter) %>%
  dplyr::rename(RMSE = rmse.test.mean) %>%
  dplyr::rename("Features (\\%)" = fw.perc) %>%
  dplyr::mutate(`Test Plot` = as.character(Plot)) %>%
  dplyr::mutate(`Test Plot` = forcats::fct_recode(`Test Plot`,
    Oiartzun = "2", Luiando = "3",
    Laukiz1 = "1", Laukiz2 = "4"
  )) %>%
  dplyr::mutate(Learner = forcats::fct_recode(Learner,
    "RF \\\\ Car" = "RF MBO Car", "XGB \\\\ Borda" = "XGBOOST MBO Borda",
    "SVM \\\\ Relief" = "SVM MBO Relief"
  )) %>%
  dplyr::mutate(Learner = as.character(Learner)) %>%
  dplyr::mutate(`Test Plot` = as.character(`Test Plot`)) %>%
  dplyr::mutate("\\#" = case_when(
    `Test Plot` == "Laukiz1" ~ ceiling(`Features (\\%)` * 559),
    `Test Plot` == "Laukiz2" ~ ceiling(`Features (\\%)` * 451),
    `Test Plot` == "Luiando" ~ ceiling(`Features (\\%)` * 301),
    `Test Plot` == "Oiartzun" ~ ceiling(`Features (\\%)` * 497),
  )) %>% 
  dplyr::group_by(Learner) %>%
  dplyr::select(Learner, `Test Plot`, "Features (\\%)", "\\#", RMSE)
